Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-11 paper/Paper.tex

Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum. Ether is the digital fuel that powers the Ethereum network. Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether. After the DAO code is deployed, ether may be sent to the DAO?s smart contract address during an initial funding period which is defined in the DAO code.

@@

DAO token holders may also submit proposals to use the DAO's ether, denoted by $\Xi_{\text{transfer}}$, for a variety of purposes. If a proposal is approved, the DAO tranmits ether to a smart contract representing the proposed project. Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
An example of such an agreement between the DAO and a project to be funded can be found in the appendix (\ref{app:SampleOffer}).

@@

A problem every that DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation. For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves. Since they would hold the majority of the tokens, they would always be able to pass their proposals.

@@

\section{Token Price} \label{TokenPrice}
DAO Token price increases over time. This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO. 
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

@@

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time as described in section \ref{TokenPrice}.

>>>>

Once deployed, the DAO code requires ``ether'' to engage in transactions on Ethereum. Ether is the digital fuel that powers the Ethereum network. Without ether, a DAO can not do very much and a DAO's first order of business is to receive ether. After the DAO code is deployed, ether may be sent to the DAO's smart contract address during an initial funding period which is defined in the DAO code.

@@

DAO token holders may also submit proposals to use the DAO's ether, denoted by $\Xi_{\text{transfer}}$, for a variety of purposes. If a proposal is approved, the DAO transmits ether to a smart contract representing the proposed project. Such smart contracts can be parameterized and enable the DAO to interact with and influence the project being funded.
An example of such an agreement between the DAO and a project to be funded can be found in the appendix (\ref{app:SampleOffer}).

@@

A problem every DAO has to mitigate is the ability for the majority to rob the minority by changing governance and ownership rules after DAO formation. For example, an attacker with $51\%$ of the tokens, acquired either during the funding period or purchased afterwards, could make a proposal to send all the funds to themselves. Since they would hold the majority of the tokens, they would always be able to pass their proposals.

@@

\section{Token Price} \label{TokenPrice}
DAO Token price increases over time. This reflects an assumption that early purchasers have greater risk, as they may have less information about the potential success of the DAO and do not know whether follow-on contribution will lead to full funding of the DAO. 
For the DAO described here, we have chosen the following price schedule:
\begin{equation}
 P(t) = \begin{cases}
0.01 & \text{if} \quad t < t_c - 2 \cdot \text{w} \\
0.01 + 0.0005 \cdot m(t) & \text{if} \quad t_c - 2 \cdot \text{w} \leqslant t < t_c - 4 \cdot \text{d} \\
0.015 & \text{otherwise}
\end{cases}
\end{equation}
with the multiplier $m$ defined as:
\begin{equation}
 m(t) = (t - (t_c - 2 \cdot \text{w})) / \text{d}
\end{equation}
Here $t$ is the unix time in seconds, $t_c$ is the closing time of the funding period (see \ref{app:TokenSale} \verb|closingTime|), $w$ is a week in seconds and $d$ a day in seconds.
Hence the number of tokens (in it’s base unit) each buyer receives is calculated as: $P(t) \cdot \Xi_c$. Here $\Xi_c$ stands for the amount of ether payed, denoted in wei.
This results in a constant price in the beginning, until $2$ weeks before the end of the token sale. At this time the price increased daily by $0.0005 \: \Xi_c$ per base unit of DAO token. Until $4$ days before the closing time when there will be a constant price of $0.015 \: \Xi_c$ per base unit of DAO token.

@@

The function \verb|buyTokenProxy| creates one unit of the DAO token’s minimum denomination for every wei sent. The price is calculated as $$\Xi_c \cdot 20 / \text{divisor}$$ Here $\Xi_c$ is the amount of wei given in order to purchase tokens, and \verb|divisor| is calculated depending on the time: $P(t) \cdot 200$ , as described in section \ref{TokenPrice}.
